Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-09-07 writeup/gz_hubble_data_draft_2.tex
Highlight changes for MiC 1.

Classifications for GZH were weighted only if the classifier was logged
into the site under their username (this was encouraged, but not required for
participation). Classifications by participants who were not logged in were marked as
``Anonymous'' and receive the same $w=1$ weighting as the vast majority of
logged-in classifiers. Results from the Galaxy Zoo: CANDELS project (Simmons et~al., submitted)
show that the distributions of weights for anonymous and
logged-in users are similar, supporting the default technique of GZH. 
% We should also try to estimate how many anonymous classifiers there were, if possible. 
% Not clear that I can do that given the SQL data

>>>>

Classifications for GZH were weighted only if the classifier was logged
into the site under their username (this was encouraged, but not required for
participation). Classifications by participants who were not logged in were marked as
``Anonymous'' and receive the same $w=1$ weighting as the vast majority of
logged-in classifiers. \changes{Results from the Galaxy Zoo: CANDELS project (Simmons et~al., submitted)
show that the distributions of weights for anonymous and
logged-in users are similar, supporting the default technique of GZH.}
% We should also try to estimate how many anonymous classifiers there were, if possible. 
% Not clear that I can do that given the SQL data
